The Effects of the NBA COVID Bubble on the NBA Playoffs

### 2020-11-13 Manuscript/NBABubbleAnalysis.Rmd
Update NBABubbleAnalysis.Rmd

# Results {#sec:results}
```{r, echo=FALSE}
#Analysis
one <- prop.test(x=c(sum(game_log_2020_home$W.L), sum(game_log_2017_2019_home$W.L)),
                 n=c(nrow(game_log_2020_home), nrow(game_log_2017_2019_home)))
X2020 <- table(game_log_2020_home$W.L)
X17_19 <- table(game_log_2017_2019_home$W.L)
homewin<- rbind(X2020, X17_19)
onew <- wilcox.test(x = game_log_2020_home$W.L, y = game_log_2017_2019_home$W.L)
rowone <- c(as.numeric(one$estimate[1]), as.numeric(one$estimate[2]), one$p.value, onew$p.value)

>>>>

# Results {#sec:results}
```{r, echo=FALSE}
#Analysis
one <- prop.test(x=c(sum(game_log_2020_home$W.L), sum(game_log_2017_2019_home$W.L)),
                 n=c(nrow(game_log_2020_home), nrow(game_log_2017_2019_home)))
X2020 <- table(game_log_2020_home$W.L)
X17_19 <- table(game_log_2017_2019_home$W.L)
homewin<- rbind(X2020, X17_19)
onew <- fisher.test(x = homewin)
rowone <- c(as.numeric(one$estimate[1]), as.numeric(one$estimate[2]), one$p.value, onew$p.value)
